---
title: "p8105_hw1_kz2383"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

problem 0.2

problem 1 part 

```{r}
install.packages("palmerpenguins")
```

```{r}
data("penguins", package = "palmerpenguins")


```
There are 8 variables in the dataset: species, island, bill_length_mm, bill_depth_mm, flipper_length_mm, baby_mass_g, sex and year.

species: It has character value,eg Adelie.
island: It has character value,eg Torgersen.
bill_length_mm: numeric value rounded to at most one decimal place. Missing value is observed.
bill_depth_mm: numeric value rounded to at most one decimal place. Missing value is observed.
flipper_length_mm: numeric value with three digits (integer). Missing value is also observed.
baby_mass_g: numeric value with four digits (integer). Missing value is also observed.
sex: character and binary value with choice of "male" and "female". Missing value is also observed.
year: four digit integer. 

There are 8 columns(variable) and 344 rows(object) in the dataset.


```{r}
library(tidyverse)
library(janitor)


penguins %>%
  janitor::clean_names()%>%
  drop_na(flipper_length_mm)%>%
  summarize(mean_flipper_length_mm = mean(flipper_length_mm)) 

penguins%>%
  ggplot(aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + 
    geom_point() +
    theme(legend.position = "bottom")

ggsave("flipper_bill.png")
```
The mean flipper length in milometer is 200.9152. A scatter plot of flipper length Vs bill length is plotted grouped by three different species. 





problem 2 part


create the  dataframe
```{r}
df=
  tibble(
    norm=rnorm(n=10),
    logical=norm>0,
    charac_vec = c("aaaaaaaaaa"),
    level=c(rep("TreatmentA",3),
                           rep("TreatmentB", 3),
                           rep("TreatmentC", 4))
    
  )
```


take mean for each variable in the dataframe


```{r, message=FALSE}
mean(pull(df,norm))
mean(pull(df,logical))
mean(pull(df,charac_vec))
mean(pull(df,level))
  
  
```
Mean for numeric value can be calculated while that for character or factor vector can't be calculated, "na"is returned as a result. 
